Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/discussions.tex

%! TEX root = icml_drau.tex
\section{Discussions}
\label{sec:discussions}
The method derived in this work seems yield improved robustness to time discretization on 
various environments, e.g. pendulum swing up, or simple locomotion tasks.
However on certain environments, there is still much room for improvment. In what follows,
we identify some of the issues that could explain this theoretical/practical discrepancy.

>>>>

%! TEX root = icml_drau.tex
\section{Discussion}
\label{sec:discussions}

The method derived in this work seems to yield improved robustness to
time discretization on various environments, e.g. pendulum swing up, or
simple locomotion tasks.  However on certain environments, there is still
room for improvment. In what follows, we identify some of the issues
that could explain this theoretical/practical discrepancy.
